### 2014-07-01 tex/main-body-text.tex
edits to conclusion section

{\sc flock} and {\sc structure} provide similar results in 
terms of how individuals are allocated among runs at low values of $K$, 
while at larger values, {\sc flock} often found, in addition to the solution identified by {\sc structure}, 
multiple other solutions. For all six groups 
of runs for \textit{k} = 2 - 4, {\sc flock} resulted in nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from results obtain from 
{\sc structure} (Fig 1). Of the 'best runs' for the six groups for $K$ = 2, two  
runs yielded identical clustering (same mean LLOD score) while all other runs 
differed by at most the allocation of 13 individuals. As 
\textit{k} increases so do the number of solutions
that {\sc flock} found (Fig 1). For all groups of runs for $K$ $\geq 2$, no plateaus were observed - all intial 
allocations resulted in solutions that differed. 
It is unclear in these cases what constitutes the 'best run' as all plateau lengths are 
equal to one. Many of these solutions are, however, suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal},
although less reliably so in the case of {\sc flock}.

Despite the similar allocation of individuals into $K$ clusters, the 
plateau analysis to estimate $K$ in {\sc flock} leads to different conclusions among groups of runs, as well as 
one that differs from {\sc structure}. While no plateaus were observed in any of the six groups 
for a $K\geq 2$, the plateau record varied greatly among each
group for $K = 2$ (plateau sequences: Run1 = 3,2,3,7,4; Run2 = 2,5,2,3,2,3; Run3 = 2,2,2,2,2,5; 
Run4 = 2,3,4,2,4,3; Run5 = 2,2,5,5,3; and; Run6 = 2,2,2,2,2,3,3). The plateau analysis 
procedure suggested by \citet{Duc&Tur2012} leads to
either an estimate of K $\geq$ 2 (Run1) or {\em undecided} as a consequence of no plateau 
lengths being greater than 6. The ($\ln P(D)$) from {\sc structure}
was largest at $K$ = 6 which was supported by the $q_i$ plots. The $\Delta K$ method, however, 
supports a $K$ = 2.

@@

To investigate the ability of the arrangement of individuals within the reference 
populations to move around the partition space we varied the number of iterations that 
each run goes through to find the 'optimal' allocation of individuals. Unfortuantely 
only the reallocation matrix for the 'best run' is given as output. Increasing the 
number of iterations did not affect the overall inference of \textit{k}. It was 
observed that often during the last iterations individuals would alternate between 
reference groups during subsequent iterations. Increasing the log likelihood 
difference threshold for reallocation to 0.18 (there needs to be at least a 1.5 times 
higher likelihood to reallocate the individual) minimized this, but did not affect the 
inference of \textit{k} (lower bound estimate of \textit{k} = 2).

@@

One of the major claimed advantages of {\sc flock} over MCMC methods for solving the 
K-partition problem is that, 'The very short processing times for each run of {\sc flock} allows for
 comparing partitions from many runs of each \textit{k}'' \citep[][p.~735]{Duc&Tur2012}.
While the authors observed improved process time in their 
comparisions we did not observe the same advantage in our analysis. In their comparison, the 
run parameters for {\sc flock} were 50 runs and 20 iterations for each \textit{k} = 1 to K+4. 
These process times were compared to the admixture model with correlated allele 
frequencies in {\sc structure} with ten iterations of a 50,000 sweep burn-in followed 
by 200,000 sweep sample from the posterior of \textit{k} from 1 to K+3. 
It seems reasonable, for each \textit{k}, to compare one iteration of {\sc structure} 
to one iteration of {\sc flock} with 50 different starting allocations that are reallocated 20 times 
as both evaluate the partition space once. Process speed advantages also may only been observed 
with low sample sizes. The authors evaluated simulated data sets with sample sizes of N = 60, 120, 
and 240.

The partition space over which {\sc flock} evaluates how individuals are clustered 
greatly increases with both the number of individuals and the number of clusters into 
which they can be partitioned. The total partition space for any given k can be 
defined by $\sum\limits_{i=1}^k S(n,k)$ where S(n,k) is a Stirling number of the 
second kind. The likelihood surface may be characterized by multiple peaks and troughs.
The peak or plateau that the  {\sc flock} algorithm finds is entirely dependent on the initial allocation of 
individuals. It is not surprising that with 2,596 individuals we could have 
drastically different plateau sequences with just two clusters and that as \textit{k} increases
{\sc flock} finds suboptimal allocations.

For those that do decide to use {\sc flock} as an alternative to {\sc structure}, the adhoc rules 
to estimate K may be overly stringent. While there has been ample 
discourse concering choosing the optimal K in  {\sc structure} \citep{Evannoetal2005, 
Pritchardetal2000, Wap&Gag2006} and \citet{Pritchardetal2000} urges users 
to be cautious of interpreting K, no such care in interpreting results 
is suggested in running {\sc flock}. The authors developed estimation rules based on simulated data 
sets with different migration regimes and rates, number of loci, and K. 
By relying on identical allocations (mean LLOD values) as a means of supporting 
a particular \textit{k},  similar but not idential 
allocations will provide no support to a given \textit{k}. This may not be as big an issue with small datasets,
however, as sample sizes increase this could have a drastic influence on the estimation of 
K.

>>>>

{\sc flock} and {\sc structure} provide similar results in 
terms of how individuals are allocated among runs at low values of $K$, 
while at larger values, {\sc flock} often found, in addition to the solution identified by {\sc structure}, 
multiple other solutions. For all six groups 
of runs for \textit{k} = 2 - 4, {\sc flock} resulted in nearly identical clustering of individuals 
(See supplementary materials) none of which differed substantially from results obtain from 
{\sc structure} (Fig 1). Of the 'best runs' for the six groups for $K$ = 2, two  
runs yielded identical clustering (same mean LLOD score) while all other runs 
differed by at most the allocation of 13 individuals. As 
\textit{k} increases so do the number of solutions
that {\sc flock} found (Fig 1). For all groups of runs for $K$ $\geq 2$, no plateaus were observed - all intial 
allocations resulted in solutions that differed. 
{\sc flock} still produces estimates of the LLOD by individual for the 
'best run', however, it is unclear in these cases what constitutes the 'best run' as all plateau lengths are 
equal to one. Many of these solutions are, however, suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal},
although less reliably so in the case of {\sc flock}.

Despite the similar allocation of individuals into $K$ clusters, the 
plateau analysis to estimate $K$ in {\sc flock} leads to different conclusions among groups of runs, as well as 
one that differs from {\sc structure}. While no plateaus were observed in any of the six groups 
for a $K\geq 2$, the plateau record varied greatly among each
group for $K = 2$ (plateau sequences: Run1 = 3,2,3,7,4; Run2 = 2,5,2,3,2,3; Run3 = 2,2,2,2,2,5; 
Run4 = 2,3,4,2,4,3; Run5 = 2,2,5,5,3; and; Run6 = 2,2,2,2,2,3,3). The plateau analysis 
procedure suggested by \citet{Duc&Tur2012} leads to
either an estimate of K $\geq$ 2 (Run1) or {\em undecided} as a consequence of no plateau 
lengths being greater than 6. The ($\ln P(D)$) from {\sc structure}
was largest at $K$ = 6 which was further supported by the $q_i$ plots, however,
the $\Delta K$ method supported a $K$ of 2.

@@

To investigate the ability of the arrangement of individuals within the reference 
populations to move around the partition space we varied the number of iterations that 
each run goes through to find the 'optimal' allocation of individuals. Unfortuantely 
only the reallocation matrix for the 'best run' is given as output. Increasing the 
number of iterations did not affect the overall inference of \textit{k}. We 
observed that often during the last iterations individuals would alternate between 
reference groups. Increasing the log likelihood 
difference threshold for reallocation to 0.18 (requiring at least a 1.5 times 
higher likelihood to reallocate the individual) minimized this, but did not affect the 
inference of \textit{k} (lower bound estimate of \textit{k} = 2).

@@

One of the major claimed advantages of {\sc flock} over MCMC methods for solving the 
K-partition problem is that, 'The very short processing times for each run of {\sc flock} allows for
 comparing partitions from many runs of each \textit{k}'' \citep[][p.~735]{Duc&Tur2012}.
While the authors observed improved process time in their 
comparisions we did not observe the same advantage in our analysis. In their comparison, the 
run parameters for {\sc flock} were 50 runs and 20 iterations for each \textit{k} = 1 to K+4. 
These process times were compared to the admixture model with correlated allele 
frequencies in {\sc structure} with ten iterations of a 50,000 sweep burn-in followed 
by a 200,000 sweep sample from the posterior of \textit{k} from 1 to K+3. 
It seemed reasonable to compare, for each \textit{k}, one iteration of {\sc structure} 
to one iteration of {\sc flock} (50 different starting allocations that are reallocated 20 times) 
as both evaluate the partition space once. The dataset used in this comparision was an order of magnatude
larger than the largest used by \citep{Duc&Tur2012} (N = 60, 120, and 240). Any process speed advantages 
may only been observed with small sample sizes.

The partition space over which {\sc flock} evaluates how individuals are clustered 
greatly increases with both the number of individuals and the number of clusters into 
which they can be partitioned. The total partition space can be 
defined by $\sum\limits_{i=1}^k S(n,k)$ where S(n,k) is a Stirling number of the 
second kind, $k$ is the number of clusters, and $n$ is the number of individuals.
The likelihood surface spanning all possible partitions
may be characterized by multiple peaks and troughs.
The peak or plateau that the  {\sc flock} algorithm finds is entirely dependent on the initial allocation of 
individuals as it has no way to visit areas of the likelihood surface with smaller values.
 It is not surprising that with 2,596 individuals we could have 
drastically different plateau sequences with just two clusters and that as \textit{k} increases
{\sc flock} finds suboptimal allocations. If the number of initial allocations does not increase
as $K$ is increased, the starting allocations become diffusely scattered in the space of all
possible partitions making it unlikely that they will converge.

For those that do decide to use {\sc flock} as an alternative to {\sc structure}, the adhoc rules 
to estimate K may be overly stringent. While there has been ample 
discourse concering choosing the optimal K in {\sc structure} \citep{Evannoetal2005, 
Pritchardetal2000, Wap&Gag2006} and \citet{Pritchardetal2000} urges users 
to be cautious of interpreting K, much less effort has been put forth examining how the number of individuals
and thenumber of starting allocations can affect not only the convergence of different runs, but also the 
inference of $K$. The authors developed estimation rules based on simulated data 
sets with a modest number of individuals and different migration regimes and rates, number of loci, and K. 
By relying on identical allocations (mean LLOD values) as a means of supporting 
a particular \textit{k},  similar but not idential 
allocations will provide no support to a given \textit{k}.
